### 2021-06-16 figures/results/tables/student_infections_table.tex
Add new figures with fixed bug in the mandatory work test scenario and fixed vaccination data (i.e. Fig 2c).

\begin{tabular}{lr}
\toprule
{} &  predicted total infections among 5-14 year olds from Easter until 2021-05-31 \\
scenario                               &                                                                               \\
\midrule
 educ open after easter  without tests &                                             705858 \\
 educ open after easter  with tests    &                                             539545 \\
 close educ after easter               &                                             414920 \\
 baseline                              &                                             425200 \\
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{lr}
\toprule
{} &  predicted total infections among 5-14 year olds from Easter until 2021-05-31 \\
scenario                               &                                                                               \\
\midrule
 educ open after easter  without tests &                                             808831 \\
 educ open after easter  with tests    &                                             627182 \\
 close educ after easter               &                                             478064 \\
 baseline                              &                                             490880 \\
\bottomrule
\end{tabular}
